An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-11 paper.tex

\section*{Introduction}
%
The collection of dynamical data during human walking has a long history
beginning with the first motion pictures and now with modern marker based
motion capture techniques, image and video analysis, and high fidelity ground
reaction load measurements. Even though years of data on thousands of subjects
now exist, this data is not widely disseminated, well organized, nor available
with few or no restrictions. David Winter's published normative gait
data~\cite{Winter1990} is widely used in biomechanics studies, yet it comes
from relatively few subjects and only a small number of gait cycles per
subject. This small source has successfully inspired powered prosthetic control
design~\cite{GoldfarbXXXX}, but success in other fields using large sets of
data for discovery lead one to believe that may be possible in the
biomechanical field too. To find out if that hypothesis is true, our data needs
to be shared extensively, organized, and curated to enabled analysts.

>>>>

\section*{Introduction}
%
The collection of dynamical data during human walking has a long history
beginning with the first motion pictures and now with modern marker based
motion capture techniques, image and video analysis, and high fidelity ground
reaction load measurements. Even though years of data on thousands of subjects
now exist, this data is not widely disseminated, well organized, nor available
with few or no restrictions. David Winter's published normative gait
data~\cite{Winter1990} is widely used in biomechanics studies, yet it comes
from relatively few subjects and only a small number of gait cycles per
subject. This small source has successfully inspired powered prosthetic control
design~\cite{Sup2008}, but success in other fields using large sets of
data for discovery lead one to believe that may be possible in the
biomechanical field too. To find out if that hypothesis is true, our data needs
to be shared extensively, organized, and curated to enabled analysts.
